\documentclass[english]{article}
\usepackage{hyperref}
\title{CIS 520, Machine Learning, Fall 2018 \\ Homework 0\\
Due: Friday, September 7th, 11:59pm \\ Submit PDF to Canvas}
\date{}

\begin{document}
\maketitle
\vspace{-30pt}
\subsection*{Collaboration Policy} 

You are allowed and encouraged to work together. You may discuss the
homework to understand the problem and reach a solution in groups up
to size {\bf four students.} However, {\em each student must write
  down the solution independently, and without referring to written
  notes from the joint session. {\bf In addition, each student must
    write on their solutions the names of people with whom they
    collaborated.}} You must understand the solution well enough 
to reconstruct it by yourself. (This is for your own benefit:
you have to take the exams alone.)

{\bf Coding assignments, unless otherwise specified, may be done
  collaboratively in teams of two (or individually)}. Teams should
submit a single codebase that clearly specifies the two
authors' names according to the assignment instructions.

\subsection*{Homework Related Questions}
If you have questions about how to approach a homework problem, you
should go to one of the many scheduled instructor/TA office hours, or post your question to Piazza. 
{\bf All questions MUST be directed to Piazza. If you send us an email, the only response you will receive is "Please post to Piazza." } If you choose, Piazza allows for you to post either anonymously or to the instructors privately.

Please refrain from posting solutions or code snippets publicly in Piazza. If you want us to review your code, please make the question private.

\subsection*{Plagiarism Policy}
When taking phrases or facts from any source (books,
articles, or the web), be sure to acknowledge where the information
was taken from.  Any text quoted directly must be enclosed in
quotation marks, again with the source noted.  The format of the
citation does not matter, as long as it is sufficiently detailed for
us to find the original source.

We will run homeworks through plagiarism detection software, and the graders will be alert for cases of copied homework.
{\bf Do not share you code or written solutions  with friends to ``let them look at it''. If they include a piece of your
homework in their submission and it is caught, you are {\it not} doing them a favor.}

Suspected violations will be reported to the Office of Student Conduct
for investigation and possible disciplinary action. We will not
contact you before reporting, but we will let you know that we have
done so.

\subsection*{Homework Submission Instructions}

All written homework {\bf must} be submitted as a PDF to Canvas. {\bf
  Handwritten assignments (scanned or otherwise) will not be
  accepted.}  We strongly encourage (if not require) the use of \LaTeX
to generate your final PDF. We will be posting the homeworks in both
PDF and \LaTeX source form, and we encourage you to use this source as
a template for your submission.

\subsection*{Student Agreement}
I have read the above policies and agree to abide by them
\\ \\
Student Name: \underline{Shubhankar Patankar}

\end{document}
